# First look at quantification of SINEs

```{r set-options, echo=FALSE}
library = function (...)
    suppressMessages(base::library(..., warn.conflicts = FALSE, quietly = TRUE))

library(modules)
import('knitr_init')
library(dplyr)
library(reshape2)
library(ggplot2)
theme_set(theme_bw())
options(stringsAsFactors = FALSE)
knitr::opts_knit$set(fig.path = 'figure/sine-',
                     cache.path = 'cache/sine-')
```

Load the result files.

```{r load-data}
result_parent = './results/bowtie/sines/express'
result_folders = list.files(result_parent, pattern = 'PolIII', include.dirs = TRUE, full.names = TRUE)
result_files = vapply(result_folders, file.path, character(1), 'results.xprs')
results = sapply(result_files, read.table, sep = '\t', header = TRUE, simplify = FALSE)
counts = `colnames<-`(sapply(results, function (x) x$tot_counts), NULL)

control_folders = list.files(result_parent, pattern = 'Input', include.dirs = TRUE, full.names = TRUE)
control_files = vapply(control_folders, file.path, character(1), 'results.xprs')
controls = sapply(control_files, read.table, sep = '\t', header = TRUE, simplify = FALSE)
control_counts = `colnames<-`(sapply(controls, function (x) x$tot_counts), NULL)
```

Merge replicates by averaging.

```{r merge-counts}
get_condition_table = function (filenames) {
    dos = sub('.*(do\\d+).*', '\\1', filenames)
    conditions = strsplit(sub('.*(brain|liver).*BL6([^_]+).*', '\\1-\\2', filenames), '-')
    tissues = sapply(conditions, function (cond) switch(cond[1], brain = 'Brain', liver = 'Liver'))
    stages = sapply(conditions, function (cond) toupper(cond[2]))
    data.frame(DO = dos, Tissue = tissues, Stage = stages, row.names = NULL) %>%
        mutate(Condition = paste(Tissue, Stage, sep = '-')) %>%
        tbl_df()
}

merge_replicates = function (counts, conditions)
    `colnames<-`(counts, conditions$DO) %>%
        melt(varnames = c('SINE', 'DO'), value.name = 'Count') %>%
        inner_join(conditions, by = 'DO', copy = TRUE) %>%
        group_by(SINE, Condition) %>%
        summarize(Count = sum(Count)) %>%
        tbl_df()

conditions = get_condition_table(result_files)
control_conditions = get_condition_table(control_files)

long_counts = merge_replicates(counts, conditions)
control_long_counts = merge_replicates(control_counts, control_conditions)
```

The distribution of counts:

```{r summary, fig.width=12}
asinh_trans = function ()
    scales::trans_new('asinh', asinh, sinh, domain = c(-Inf, Inf))

scale_y_asinh = function (...)
    scale_y_continuous(..., trans = asinh_trans())

total_counts = rbind_list(mutate(long_counts, Experiment = 'PolIII'),
                          mutate(control_long_counts, Experiment = 'Input'))

ggplot(total_counts, aes(x = Condition, y = Count)) +
    geom_boxplot(aes(fill = Experiment)) +
    scale_y_asinh()

ggplot(filter(total_counts, Count != 0), aes(x = Condition, y = Count)) +
    geom_boxplot(aes(fill = Experiment)) +
    scale_y_asinh(name = 'Counts (without zeros)')
```

Clearly the input libraries have substantial spurious binding. We subtract
those from the raw counts.

```{r confident-counts, fig.width=8}
confident_counts = long_counts %>%
    inner_join(rename(control_long_counts, InputCount = Count),
               by = c('SINE', 'Condition')) %>%
    mutate(Count = sapply(Count - InputCount, max, 0)) %>%
    select(-InputCount)

ggplot(confident_counts, aes(x = Condition, y = Count)) +
    geom_boxplot() +
    scale_y_asinh()
```

To assess how much binding differs between individual classes of SINEs, we sum
over all conditions and show the distribution of read counts on SINE classes.
We discard the lower quartile to get a more manageable distribution display.

```{r counts-per-sine, fig.width=12}
counts_per_sine = confident_counts %>%
    group_by(SINE) %>%
    summarize(Count = sum(Count))

without_lower_q = counts_per_sine %>% filter(Count > quantile(Count, 0.25))
ggplot(without_lower_q, aes(Count)) + geom_histogram(binwidth = 5000)
```

We can also look at how the counts differ across conditions: first across
tissues, and then across stages.

```{r counts-per-condition, fig.width=12}
counts_over_condition = confident_counts %>%
    mutate(Tissue = sapply(strsplit(Condition, '-'), function (x) x[1]),
           Stage = sapply(strsplit(Condition, '-'), function (x) x[2]))

ggplot(counts_over_condition, aes(Count, fill = Tissue)) +
    geom_density(adjust = 10, position = 'fill', size = 0)

ggplot(counts_over_condition, aes(Count, fill = Stage)) +
    geom_density(adjust = 10, position = 'fill', size = 0)
```
