# First look at quantification of SINEs

```{r echo=FALSE}
library(modules)
import('knitr_init')
library(dplyr)
```

We look at tRNA derived (or something like that) SINEs only at first, since their number is already quite large.

```{r results='asis'}
filename = './results/tophat-old/coverage/do2011.sine-trna.coverage'
data = read.table(filename, sep = '\t', header = FALSE, stringsAsFactors = FALSE)
kable(head(data))
```

This file was generated via `bedtools coverage`.
Column `V10` is the read count overlapping with the feature in that row. Here’s a rough overview:

```{r}
hist(data$V10, ylim = c(0, 100), breaks = 20, col = 'grey', border = 'grey')
```

Let’s look at the genes with more than 20 mapping reads. But first, get rid of useless columns.

```{r results='asis'}
colnames(data) = c('Chr', 'Generator', 'Type', 'Start', 'End' , 'Score',
                   'Strand', 'Frame', 'Attributes', 'Count', 'BasesCovered',
                   'FeatureLength', 'FractionCovered')
data = select(data, Chr, Start, End, Type, Attributes, Count, BasesCovered)

top_expressed = filter(data, Count >= 20)
kable(top_expressed)
```
