```{r init, results='hide'}
modules::import('./knit')
```

We summarised the data in a previous analysis step, so we can just load it now.
We aren’t going to use all columns, so throw out what’s unnecessary
immediately.

```{r load-data}
stage_levels = c('E15.5', 'E18.5', 'P0.5', 'P4', 'P22', 'P29')
(data = tbl_df(io$read_table('./results/coverage-summary-all.tsv',
                             header = TRUE)) %>%
    select(-BasesCovered) %>%
    mutate(Stage = factor(Stage, stage_levels)))
```

Some of the features are annotated in a way that is not immediately usable
here. We will merge the different biotype annotations belonging in the same
category, putative repeats, and discard the (redundant) rRNA and snRNA
annotations in the repeats feature set (biotypes taken from
http://www.gencodegenes.org/gencode_biotypes.html).

```{r sanitize-data}
merge_features = function (data, ...) {
    dots = list(...)
    new_name = names(dots)
    features = dots[[1]]
    stopifnot(length(new_name) == 1)
    new_feature = data %>%
        filter_(bquote(Feature %in% .(features))) %>%
        group_by(DO, IP, Tissue, Stage) %>%
        summarise_each(funs(sum), -Feature, -Type) %>%
        mutate(Feature = new_name)
    data = data %>%
        filter_(bquote(! Feature %in% .(features)))

    bind_rows(data, new_feature)
}

all_trnas = unique(filter(data, Type == 'trnas')$Feature)
non_repeats = c('rRNA', 'snRNA', 'tRNA', 'srpRNA', 'scRNA')
sanitized = data %>%
    filter(! (Type == 'repeats' & Feature %in% non_repeats)) %>%
    merge_features(`repeat` = c('Unknown', 'Other', 'DNA', 'DNA?', 'RNA',
                                'Low_complexity', 'RC', 'RC?')) %>%
    merge_features(SINE = c('SINE', 'SINE?')) %>%
    merge_features(LTR = c('LTR', 'LTR?')) %>%
    merge_features(RC = c('RC', 'RC?')) %>%

    merge_features(`protein-coding` = c('IG_C_gene', 'IG_D_gene', 'IG_J_gene',
                                        'IG_LV_gene', 'IG_V_gene', 'TR_V_gene',
                                        'protein_coding')) %>%
    merge_features(ncRNA = c('3prime_overlapping_ncrna', 'antisense',
                             'lincRNA', 'processed_transcript',
                             'sense_intronic', 'sense_overlapping',
                             'miRNA', 'misc_RNA', 'snoRNA', 'snRNA')) %>%
    merge_features(pseudogene = c('IG_V_pseudogene', 'TR_V_pseudogene',
                                  'polymorphic_pseudogene', 'pseudogene')) %>%
    merge_features(tRNA = all_trnas) %>%
    select(-Type)
```

Library size normalise the data by dividing the coverage in each sample by the
sum of the coverage over all its features.

```{r normalize}
normalized = sanitized %>%
    group_by(DO) %>%
    mutate(LogCoveragePerBase = log(Coverage) - log(BasesTotal)) %>%
    mutate(TPM = exp(LogCoveragePerBase - log(sum(exp(LogCoveragePerBase))) + log(1E6))) %>%
    select(-LogCoveragePerBase) %>%
    ungroup()
```

Average over replicates.

```{r average-replicates}
# Helper function that summarises a vector of all equal elements by picking the
# first element, all the while ensuring that all elements are in fact equal.
all_same = function (data) {
    stopifnot(length(unique(data)) == 1)
    first(data)
}

averaged = normalized %>%
    group_by(Feature, IP, Tissue, Stage) %>%
    summarize(Coverage = mean(Coverage),
              TPM = mean(TPM),
              BasesTotal = all_same(BasesTotal)) %>%
    ungroup()
```

Plot fraction of binding to each feature, for each stage (we are just
interested in liver). Display only the top 10 highly covered features.

```{r plot, fig.width=12}
get_plot_data = function (data, criteria, counts_col_name = 'TPM') {
    stopifnot(inherits(criteria, 'formula'))
    used_data = filter_(data, criteria)
    top_features = used_data %>%
        group_by(Feature) %>%
        summarize_(Counts = bquote(mean(.(as.name(counts_col_name))))) %>%
        arrange(desc(Counts)) %>%
        .$Feature
    used_data %>%
        rename_(Counts = counts_col_name) %>%
        mutate(Feature = factor(Feature, top_features, ordered = TRUE)) %>%
        mutate(Order = as.integer(Feature)) %>%
        arrange(Order)
}

liver_pol3 = get_plot_data(averaged, ~(IP == 'PolIII' & Tissue == 'Liver'))

library(RColorBrewer)
fill_scale = c(brewer.pal(10, 'Set3'), '#F0F0F0')

plot_coverage = function (data)
    ggplot(data, aes(Stage, Counts)) +
        geom_bar(aes(fill = Feature), stat = 'identity', position = 'fill') +
        scale_y_continuous(name = 'Relative abundance of binding') +
        scale_fill_manual(values = fill_scale) +
        theme(panel.border = element_blank(),
              panel.grid.minor = element_blank(),
              panel.grid.major.x = element_blank())

plot_coverage(liver_pol3)
```

Let’s double-check this with the inputs:

```{r plot-inputs, fig.width=12}
liver_input = get_plot_data(averaged, ~(IP == 'Input' & Tissue == 'Liver'))
plot_coverage(liver_input)
```

The absurd overrepresentation of “Satellite” elements justifies excluding this
element from the analysis (in the absence of a good mechanism for background
noise from the coverage data).

```{r plot-no-satellite, fig.width=12}
nosat = filter(averaged, Feature != 'Satellite')
liver_pol3_nosat = get_plot_data(nosat, ~(IP == 'PolIII' & Tissue == 'Liver'))
plot_coverage(liver_pol3_nosat)
```

Unfortunately this is very much uninformative, besides telling us that most of
the transcription is of tRNA. Let’s plot absolute coverage instead.

```{r plot-absolute, fig.width=12}
absolute = get_plot_data(nosat, ~(IP == 'PolIII' & Tissue == 'Liver'), 'Coverage')
plot_coverage(absolute)
```

… which apparently mainly shows genomic feature length rather than anything
about coverage. This becomes obvious when comparing the coverage with that of
the inputs:

```{r plot-absolute-inputs, fig.width=12}
absolute_input = get_plot_data(nosat, ~(IP == 'Input' & Tissue == 'Liver'), 'Coverage')
plot_coverage(absolute_input)
```

Hence that plot is not interpretable. Until I’ve figured out how to deal with
the input data, I’ll go with the TPMs.

Remove tRNA from the display to zoom in on rest.

```{r plot-no-trna, fig.width=12}
notrna = filter(nosat, Feature != 'tRNA')
liver_notrna =  get_plot_data(notrna, ~(IP == 'PolIII' & Tissue == 'Liver'))
plot_coverage(liver_notrna)
```
