```{r init}
modules::import('./knit')
```

We summarised the data in a previous analysis step, so we can just load it now.
We aren’t going to use all columns, so throw out what’s unnecessary
immediately.

```{r load-data}
(data = tbl_df(io$read_table('./results/coverage-summary-all.tsv',
                             header = TRUE)) %>%
    select(-BasesCovered) %>%
    mutate(Stage = factor(Stage, c('E15.5', 'E18.5', 'P0.5', 'P4', 'P22', 'P29'))))
```

Some of the features are annotated in a way that is not immediately usable
here. We will merge the different IG annotations, “SINE” and “SINE?”, “LTR” and
“LTR?”, “RC” and “RC?”, and discard the (redundant) rRNA and snRNA annotations
in the repeats feature set.

```{r sanitize-data}
merge_features = function (data, ...) {
    dots = list(...)
    new_name = names(dots)
    features = dots[[1]]
    stopifnot(length(new_name) == 1)
    new_feature = data %>%
        filter_(bquote(Feature %in% .(features))) %>%
        group_by(DO, IP, Tissue, Stage) %>%
        summarise_each(funs(sum), -Feature, -Type) %>%
        mutate(Feature = new_name)
    data = data %>%
        filter_(bquote(! Feature %in% .(features)))

    bind_rows(data, new_feature)
}

sanitized = data %>%
    filter(Type == 'gene' | ! Feature %in% c('rRNA', 'snRNA')) %>%
    merge_features(SINE = c('SINE', 'SINE?')) %>%
    merge_features(LTR = c('LTR', 'LTR?')) %>%
    merge_features(RC = c('RC', 'RC?')) %>%
    merge_features(IG = c('IG_C_gene', 'IG_D_gene', 'IG_J_gene', 'IG_LV_gene',
                          'IG_V_gene')) %>%
    select(-Type)
```

Library size normalise the data by dividing the coverage in each sample by the
sum of the coverage over all its features.

```{r normalize}
normalized = sanitized %>%
    group_by(DO) %>%
    mutate(LogCoveragePerBase = log(Coverage) - log(BasesTotal)) %>%
    mutate(TPM = exp(LogCoveragePerBase - log(sum(exp(LogCoveragePerBase))) + log(1E6))) %>%
    select(-LogCoveragePerBase) %>%
    ungroup()
```

Average over replicates.

```{r average-replicates}
# Helper function that summarises a vector of all equal elements by picking the
# first element, all the while ensuring that all elements are in fact equal.
all_same = function (data) {
    stopifnot(length(unique(data)) == 1)
    first(data)
}

averaged = normalized %>%
    group_by(Feature, IP, Tissue, Stage) %>%
    summarize(Coverage = mean(Coverage),
              TPM = mean(TPM),
              BasesTotal = all_same(BasesTotal)) %>%
    ungroup()
```

Plot fraction of binding to each feature, for each stage (we are just
interested in liver). Display only the top 10 highly covered features.

```{r plot, fig.width=12}
top_10 = averaged %>%
    filter(IP == 'PolIII', Tissue == 'Liver') %>%
    group_by(Feature) %>%
    summarize(TPM = mean(TPM)) %>%
    arrange(desc(TPM)) %>%
    top_n(10, TPM) %>%
    .$Feature

get_plot_data = function (data, criteria, top_features) {
    stopifnot(inherits(criteria, 'formula'))
    data %>%
    filter_(criteria) %>%
    filter(Feature %in% top_features) %>%
    mutate(Feature = factor(Feature, top_features, ordered = TRUE)) %>%
    mutate(Order = as.integer(Feature)) %>%
    arrange(Order)
}

liver_pol3 = get_plot_data(averaged,
                           ~(IP == 'PolIII' & Tissue == 'Liver'), top_10)

plot_coverage = function (data)
    ggplot(data, aes(Stage, TPM)) +
        geom_bar(aes(fill = Feature), stat = 'identity', position = 'fill') +
        scale_y_continuous(name = 'Relative abundance of binding') +
        scale_fill_brewer(palette = 'Set3')

plot_coverage(liver_pol3)
```

Let’s double-check this with the inputs:

```{r plot-inputs, fig.width=12}
liver_input = get_plot_data(averaged,
                            ~(IP == 'Input' & Tissue == 'Liver'), top_10)

plot_coverage(liver_input)
```
