```{r echo=FALSE}
modules::import('knit')
```

We have generated coverage for all annotated features of diverse feature types
in an upstream step of the analysis. In this step, we aggregate all those
different loci on a per-feature. This is done for each sample. The summary
coverage file is manageable enough in terms of size to be easily transmitted.

Since the total size of the files on disk is just shy of 10 GiB, we will
perform the analysis per-file (i.e. per sample/feature type) rather than all at
once. As a consequence, the subsequent code is wholly wrapped inside functions.

Load the coverage data for a single sample and one super-type of feature (genes
or repeats), discard all non-autosomal data:

```{r read-coverage-file}
read_coverage_file = function (filename)
    io$read_table(filename, header = FALSE) %>%
    select(Chr = 1, Feature = 4, Coverage = 5, BasesCovered = 6,
           BasesTotal = 7) %>%
    filter(grep('^\\d+$', Chr)) %>%
    select(-Chr) %>%
    tbl_df()
```

(We left off the last column since it’s just `BasesCovered / BasesTotal`.

Aggregate a single coverage table:

```{r aggregate-coverage}
aggregate_coverage = function (coverage)
    coverage %>%
    group_by(Feature) %>%
    summarise_each(funs(sum), -Feature)
```

Merge the two super-type coverage tables for a single sample:

```{r collate-annotations}
collate_annotations = function (genes, repeats)
    rbind_list(genes, repeats)
```

Of course we need to test this. So here goes.

```{r test-run}
coverage_path = 'results/bowtie/coverage'
test1_file_genes = 'do1537_PolIII_brain_1900_mmuBL6e15.5_CRI01_genes.counts'
test1_file_repeats = 'do1537_PolIII_brain_1900_mmuBL6e15.5_CRI01_repeats.counts'
test1_genes = read_coverage_file(file.path(coverage_path, test1_file_genes))
test1_repeats = read_coverage_file(file.path(coverage_path, test1_file_repeats))
test1_genes_aggregate = aggregate_coverage(test1_genes)
test1_repeats_aggregate = aggregate_coverage(test1_repeats)
test1 = collate_annotations(test1_genes_aggregate, test1_repeats_aggregate)
```

---

Now we prepare the actual analysis by listing and categorising the input files
by sample and feature (super) type.

```{r setup}
all_files = list.files(coverage_path)
info = as.data.frame(do.call(rbind, strsplit(all_files, '_'))) %>%
    select(DO = 1, IP = 2, Tissue = 3, Stage = 5, Type = 7) %>%
    mutate(IP = ifelse(IP == 'polIII', 'PolIII', IP)) %>%
    mutate(Tissue = sapply(Tissue, switch, liver = 'Liver', brain = 'Brain')) %>%
    mutate(Stage = toupper(sub('^MMUS?BL6', '', Stage, ignore.case = TRUE))) %>%
    mutate(Type = sub('\\.counts$', '', Type)) %>%
    mutate(Filename = all_files) %>%
    tbl_df()
```

Now we run this on all the data, in parallel. Collate all the results into one
big (long format) table.

```{r analysis}
full_paths = file.path(coverage_path, all_files)
cores = as.integer(Sys.getenv('LSB_MAX_NUM_PROCESSORS', parallel::detectCores()))
results = parallel::mclapply(full_paths,
                             aggregate_coverage %.% read_coverage_file,
                             mc.cores = cores) %>%
    {Map(function (a, b) cbind(a, Filename = b), ., all_files)} %>%
    {do.call(rbind_list, .)} %>%
    inner_join(info, by = 'Filename') %>%
    select(-Filename)
```

Finally, save the result.

```{r safe-result, cache=FALSE}
io$write_table(results, './results/coverage-summary-all.tsv')
```
